A boundary integral equation approach to computing eigenvalues of the Stokes operator

### 2019-03-25 doc/draft-01-stokes/01intro.tex
update paper, add references, add conclusion

While integral equation based methods for the
related ``buckling'' eigenvalue problem
have been considered previously,
these typically relied on first-kind integral
equation formulations of the underlying PDE,
i.e. formulations in which the BIE operator is
compact \cite{kitahara2014boundary,antunes2011buckling}.
%
This is unsatisfying from a theoretical
perspective, because such operators are never \note{Travis: why is this the case?} 
invertible
(though, they are not injective precisely when $k^2$ is an
eigenvalue \cite{kitahara2014boundary,antunes2011buckling})
so that the relation between the non-invertibility of the
discrete system and the eigenvalues is obscured.
%
Further,
such representations create numerical challenges because
common measures of the ``non-invertibility'' of a matrix,
like the smallest singular value or the determinant, converge
rapidly to zero for all values of $k^2$ as the boundary is
refined. Therefore, the measure of whether $k^2$ is an
approximate eigenvalue is {\em relative to the current grid}
for first kind equations.

>>>>

While integral equation based methods for the
equivalent \cite{kelliher2009eigenvalue}
``buckling'' eigenvalue problem
have been considered previously,
these typically relied on first-kind integral
equation formulations of the underlying PDE,
i.e. formulations in which the BIE operator is
compact \cite{kitahara2014boundary,antunes2011buckling}.
%
This is unsatisfying from a theoretical
perspective, because compact operators always
have nontrivial nullspaces
(though, by design, the representations in
\cite{kitahara2014boundary,antunes2011buckling}
are not injective precisely when
$k^2$ is an eigenvalue).
%
This obscures the relation between
the non-invertibility of the
discrete system and the eigenvalues;
in particular, common measures of the
``non-invertibility'' of a matrix, like the
smallest singular value or the determinant,
converge rapidly to zero for all values
of $k^2$ as the boundary is refined.
The measure of whether $k^2$ is an
approximate eigenvalue is then {\em relative to the
  current grid} for first kind formulations.

### 2019-03-25 doc/draft-01-stokes/03analysis.tex
update paper, add references, add conclusion

\begin{remark}
In practice, using Kress-quadrature for large
problems is problematic owing to the global
nature of the quadrature rule.
Coupling with fast direct solvers for computing determinants also results in $O(N^2 \log{N})$.
where $N$ is the number of discretization points on the boundary.
Typical fast direct solvers
query $O(N)$ matrix entries to obtain a compressed representation,
this combined with the fact that evaluating each matrix entry
costs $O(N)$ for Kress-quadratures results in the sub-optimal
complexity. 
Over the last two decades, many high-order quadrature methods which are compatible with
fast algorithms like the fast multipole method (and fast direct solvers as well, 
since each matrix entry requires O(1) work) have been developed for solving
integral equations.
Extensive numerical evidence suggests that the zeros of the 
determinants of linear systems discretized using 
these quadrature methods are also high order approximations of Dirichlet eigenvalues
for the Stokes PDE--- the error is observed to be proportional to the quadrature error
for the eigenfunction $\bt^{-}$ associated with the eigenvalue.
We leave a proof of this to future work.
\end{remark}

>>>>

\begin{remark}
In practice, using Kress quadrature for large
problems is problematic owing to the global
nature of the quadrature rule.
%
First, the use of a global rule does not allow
for adaptive refinement at a complicated, local
feature of the boundary.
%
Second, the integration weight in each entry
of the matrix depends on both the column and the row
in a non-separable way.
%
As a result, the fast multipole method is not
directly applicable to the resulting matrix
and many fast-direct methods for computing
the determinant lose efficiency (for
instance, the reasoning behind the use of a
{\em proxy surface} \cite{cheng2005compression}
no longer holds).
%
%Coupling with fast direct solvers for computing determinants also results in $O(N^2 \log{N})$.
%where $N$ is the number of discretization points on the boundary.
%Typical fast direct solvers
%query $O(N)$ matrix entries to obtain a compressed representation,
%this combined with the fact that evaluating each matrix entry
%costs $O(N)$ for Kress quadratures results in the sub-optimal
%complexity. 
Over the last two decades, many high-order quadrature
methods which are compatible with
the fast multipole method and fast-direct solvers
have been developed.
%
Extensive numerical evidence suggests that the zeros of the 
determinants of linear systems discretized using 
these quadrature methods are also high order approximations
of Dirichlet eigenvalues for the Stokes operator ---
the error is observed to be proportional to the quadrature error
for the eigenfunction $\bt^{-}$ associated with the eigenvalue.
We leave a proof of this to future work.
\end{remark}
